---
title: "Presentation pitch"
author: "icg"
date: "8/25/2020"
output: slidy_presentation
mode: standalone
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(tidyverse)
library(knitr) 
```


## Introduction

The shiny app is a basic data exploration tool. 

It allows a visual inspection of the variables of a dataset, using univariate and bivariate plots. 

```{r}
data ("iris")

ggplot(data = iris, 
       aes(x = Sepal.Length, 
             y = Sepal.Width, 
             color = Species)) + 
   geom_point() +
   theme_minimal()

```


---
 
## App contents
 
The app contains a sidebar and 4 tabs:

> - Sidebar: contains two widgets to select the variables
> - Tab 1: Instructions to use the app
> - Tab 2: univariate plots for selected variables
> - Tab 3: bivariate plot for selected variables
> - Tab 4: mean ratio between selected variables

--- 

## Iris data

The app runs on the iris data, but it can be easily adapted to present any other data set. The ploting functions is ggplot2::qplot, which chooses the most adequate geom depending on the class of the selected variables: 

```{r}
as_tibble(iris) %>% 
   kable(.)
```

##  

Thank you!
